\documentclass[14pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{color}
\usepackage{hyperref}
\usepackage{tabularx}

\name{Nageswara Rao}{Maridu}
\newcommand{\project}[5]{
    \noindent
    \begin{tabularx}{\textwidth}{Xr}
    \textbf{#1} & \textit{#2} \\
    \end{tabularx}
    #3 \\ % Project description
    \noindent\textbf{Stack:} \textbf{#4} % Tech stack in bold
    \begin{itemize}[label=\textbullet, left=1em] % Solid bullet points and left padding
    #5 % Responsibilities as bullet points
    \end{itemize}
    \vspace{1em} % Add some space after each project
}
\newcommand*{\customcventry}[7][.13em]{
    \begin{tabular}{@{}l}
    {\bfseries #4} \
        {\itshape #3}
    \end{tabular}
    \hfill
    \begin{tabular}{l@{}}
    {\bfseries #5} \
        {\itshape #2}
    \end{tabular}
    \ifx
        &#7&%
    \else
            {\
        \begin{minipage}{\maincolumnwidth}%
        \small#7%
        \end{minipage}}
    \fi%
    \par\addvspace{#1}}
\begin{document}
    \makecvtitle
    \vspace*{-17mm}
    \begin{center}
        \textbf{ Senior Software Engineer II(Staff)}
    \end{center}
    \begin{center}
        \begin{tabular}{ c c c }
            \faMobile\enspace +1 587-969-9556& \enspace\faEnvelope\enspace maridu.nageswararao@gmail.com& \enspace\faHome\enspace Calgary, Alberta, Canada\\
        \end{tabular}
    \end{center}
    \begin{center}
        \begin{tabular}{ c c c }
            \faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/nrmaridu/}{in/nrmaridu} &
            \enspace \faGithub\enspace \color{blue} \href{https://github.com/nrmaridu}{github.com/nrmaridu} &
            \enspace \faLanguage\enspace \color{blue} \href{https://www.loc.gov/standards/iso639-2/php/langcodes_name.php?iso_639_1=en}{en},
            \href{https://www.loc.gov/standards/iso639-2/php/langcodes_name.php?iso_639_1=te}{te}
        \end{tabular}
    \end{center}
    \section{Profile}
    {Results-oriented and innovative Senior Software Engineer with \textbf{10} years of
    expertise, specializing in building large scale cloud native SaaS solutions with \textbf{microservices} architecture.
    Responsible and articulate individual with strengths in System Design, Solution Optimization, Cloud, Microservices architecture and Domain Driven Design.}
    \vspace{0.5em}

    {Seeking a challenging senior/lead role in distributed system projects where I can utilize my
    experience to drive innovation and contribute to the success of projects.}

    \section{Areas of Expertise}
    {Software Development - Distributed Systems - Microservices - Cloud Computing - Object Oriented Design - Concurrent Programming - REST - Event Driven Architecture - IAM - DDD - TDD}


    \section{Work Experience}

    \customcventry{Oct 2022 ‐ Present}{{\color{blue}\href{https://www.blackduck.com/}{Blak Duck Software}}}{Staff Software Engineer}{Calgary, AB, Canada}{}{}

    \customcventry{Jan 2022 ‐ Sep 2024}{{\color{blue}\href{https://www.synopsys.com/}{Synopsys Canada}}}{Staff Software Engineer}{Calgary, AB, Canada}{}{}

    \customcventry{Dec 2016 ‐ Jan 2022}{{\color{blue}\href{https://www.synopsys.com/}{Synopsys India Pvt Ltd}}}{Software Engineer (I, II \& Senior)}{Bangalore, KA, India}{}{}

    \customcventry{June 2016 ‐ Nov 2016}{{\color{blue}\href{https://www.synopsys.com/}{Cigital Asia Pvt Ltd (now Synopsys)}}}{Associate Software Engineer}{Bangalore, KA, India}{}{}

    \customcventry{Oct 2014 ‐ May 2016}{{\color{blue}\href{https://atos.net/en/}{Syntel Pvt Ltd  (now Atos)}}}{Application Programmer}{Chennai,TN, India}{}{}


    \section{Projects}

    % Polaris NG Project
    \project{Polaris Nextgen}{Dev 2020 ‐ present}
    {Polaris is an integrated, cloud-based SaaS application security testing solution designed specifically for DevSecOps and development teams.
    I'm the lead developer responsible for design and development of SCM integration, Audit, Notification and IAM microservices for the platform.}
    {Java, Golang, Spring Boot, Postgres, jOOQ, Rabbit MQ, Redis, Kubernetes, Datadog, RHSSO, Auth0}
    {
        \item Designed and developed a microservice for seamless integrations between Polaris and popular SCM platforms like GitHub, GitLab, and Azure, enabling real-time scanning of source code and automated security testing.
        \item Developed a Golang based SCM Runner module that securely pulls source code from various platforms (e.g. GitHub) and uploads it to Google Cloud Storage.
        \item Developed a Golang library to upload large files to Cloud storage  using resumable upload feature, enabling efficient and reliable file uploads.
        \item Played a crucial role in resolving critical issues in Polaris Audit Service, enabling successful closure of a key deal, and led the design of self-serviceable audit logging capabilities that significantly reduced manual effort and improved overall operational efficiency.
        \item Led the redesign of Polaris email notifications, introducing a template engine for efficient email template management, and modularized the notification service code base using Domain-Driven Design (DDD), while also developing an end-to-end test suite to ensure seamless workflow testing.
        \item Demonstrated quick domain expertise in Identity and Access Management(IAM) and led the transition from RHSSO to Auth0 IDP, successfully delivering user management and login workflows using Auth0, as well as critical features like Kong and Auth0 integration.
        \item Guided junior developers, offering implementation advice and serving as a key technical resource. Fostered team skill development and knowledge sharing.
    }

    \newpage

    % Reporting Platform Project
    \project{Reporting Platform}{Mar 2018 ‐ Nov 2020}
    {Reporting platform is a cloud-based SaaS platform that provides key insights on software risks, aggregating security vulnerabilities from multiple sources into a single dashboard for visualization. I played a crucial role in bringing this idea to life by understanding marketing professionals' requirements, designing and developing the solution.}
    {Java, Spring Boot, Spring Batch, Postgres, jOOQ, Rabbit MQ, Redis, Kubernetes, New Relic}
    {
        \item Contributed to product design ideas with marketing and sales teams, as well as architects, ensuring a cohesive vision for the platform. Quickly delivered a proof of concept within a month, demonstrating the feasibility of the idea.
        \item Proposed a solution that was widely accepted by the entire team, showcasing my ability to drive consensus and deliver results. This design laid the foundation for the successful implementation of the Reporting Platform.
        \item Introduced the innovative idea of designing agents for fetching software vulnerabilities from different sources, which was widely appreciated by the team and stakeholders. This creative solution helped differentiate our platform and improve its capabilities.
        \item Led the technical aspects of the project with a team of 5 backend developers, overseeing the development process to ensure timely and accurate delivery. Successfully brought the project live within 6 months, providing a strategic advantage for the SIG team by ranking top-right in the Gartner magic quadrant.
        \item Guided fellow developers on the technology stack used in the project, sharing knowledge and expertise to ensure successful implementation. Demonstrated strong leadership skills by empowering team members and fostering a collaborative environment.
    }

    % Cigital Projects
    \project{Software Security Application Suite}{June 2016 ‐ Feb 2018}
    {As a Full Stack Developer at Cigital, I contributed to the development of several software security applications.}
    {Java, Spring Boot, JSP, MySQL, REST API, JavaScript, Bootstrap, Angular 2+}
    {
        \item Designed and developed multiple full-stack applications using a range of technologies..
        \item Led the transformation of a JavaScript based frontend application to Angular 2+ for a project, while assisting fellow developers in writing efficient and maintainable code.
        \item Made a significant impact by quickly acquiring expertise in Angular 2+, leveraging it's features and best practices to drive project success.
        \item Demonstrated expertise in migrating existing authorization model from RBAC to the new PBAC model using spring security framework.
    }

    % Syntel Project
    \project{Plan Sponsor Application}{Oct 2014 ‐ May 2016}
    {In my early years as a software professional, I worked as an outsourced Applications Programmer for Manulife, a Canadian multinational insurance company in modernizing their retirement plan service applications.}
    {Java, Spring Boot, Spring Batch, Postgres, jOOQ, Rabbit MQ, Redis, Kubernetes, New Relic}
    {
        \item Enhanced multiple backend applications to improve performance and efficiency..
        \item Migrated the legacy HTML/CSS based front-end to a modern Bootstrap 5 based frontend, ensuring a seamless user experience across multiple browsers.
        \item Designed multi-browser compatible UI components using JavaScript and jQuery, streamlining the development process.
        \item Developed shell scripts and Ant scripts to automate local development processes, significantly increasing developer productivity.
    }

    \newpage{}

    \section{Education}
    \customcventry{2008-2014}{\color{blue}\href{https://www.google.com/}{Rajiv Gandhi University of Knowledge Technologies}}{Integrated Dual Degree}{Nuzvid, India}{}{CGPA : 8.15/10}{Bachelor of Technology in Computer Science \& Engineering | Minor in Management Studies.}

    \section{Skills}
    {\begin{itemize}[label=\textbullet]
         \itemsep0em
         \item {\textbf{Java}(primary), \textbf{Golang}, Python, JavaScript}
         \item {\textbf{PostgreSQL}, MySQL}
         \item {\textbf{Docker, Kubernetes, GCP, Cloud Run, Kubernetes Jobs, Google Cloud Storage }}
         \item {\textbf{RabbitMQ, Redis, Datadog(Log Monitoring)}}
         \item {\textbf{REST}, gRPC API development}
         \item {Event Driven \textbf{Microservices} Development }
         \item {\textbf{Domain Driven Design(DDD)}}
         \item {\textbf{Identity and Access Management (IAM)}, with expertise in authentication, authorization, and access control}
    \end{itemize}}


    \section{Achievements}
    \customcventry{Oct 2023}{{\color{blue}\href{https://www.synopsys.com/}{(Synopsys Inc)}}}{Ace Award}{Calgary, AB, Canada}{}{
            {Awarded the Ace Award for Outstanding Performance, recognizing my exceptional contributions to the team. Notable achievements include:}
            {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
                 \item Rapidly gaining expertise in Audit and Notifications domains, consistently delivering crucial features.
                 \item Successfully addressing complex consumer issues that significantly contributed to closing major deals.
                 \item Improving system design to accommodate innovative solutions, ensuring smooth progression of essential functionalities.
        \end{itemize}}
        \text{This achievement showcases my ability to adapt quickly, think critically, and drive results.}
    }

    \vspace{1em}

    \customcventry{Aug 2019}
    {{\color{blue}\href{https://www.synopsys.com/}{(Synopsys Inc)}}}{Star Award}{Bangalore, KA, India}{}{
            {Recipient of the Star Award in individual category, recognizing my extraordinary performance in designing and developing the Reporting Platform for Software Security Vulnerabilities. Notable achievements include:}
            {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
                 \item Played a crucial role in designing and implementing the reporting platform, extracting data from multiple sources using batch pattern within a short span.
                 \item Demonstrated exceptional expertise and problem-solving skills in integrating diverse data streams to provide actionable insights.
        \end{itemize}}
            {This achievement highlights my ability to drive complex projects forward, think creatively, and deliver high-quality results
        under tight deadlines.}
    }

\end{document}



