\documentclass[14pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{color}
\usepackage{hyperref}
\usepackage{tabularx}

\name{Nageswara Rao}{Maridu}
\newcommand{\projectdesc}[1]{\fontsize{1.2em}{8em}\selectfont #1}
\newcommand{\project}[5]{
    \noindent
    \begin{tabularx}{\textwidth}{Xr}
    \textbf{#1} & \textit{#2} \\
    \end{tabularx}
    #3 \\ % Project description
    \noindent\textbf{Stack:} #4 % Tech stack in bold
    \begin{itemize}[label=\textbullet, left=1em] % Solid bullet points and left padding
    #5 % Responsibilities as bullet points
    \end{itemize}
    \vspace{1em} % Add some space after each project
}
\newcommand*{\customcventry}[7][.13em]{
    \begin{tabular}{@{}l}
    {\bfseries #4} \
        {\itshape #3}
    \end{tabular}
    \hfill
    \begin{tabular}{l@{}}
    {\bfseries #5} \
        {\itshape #2}
    \end{tabular}
    \ifx
        &#7&%
    \else
            {\
        \begin{minipage}{\maincolumnwidth}%
        \small#7%
        \end{minipage}}
    \fi%
    \par\addvspace{#1}}
\begin{document}
    \makecvtitle
    \vspace*{-17mm}
    \begin{center}
        \textbf{ Senior Software Engineer II(Staff)}
    \end{center}
    \begin{center}
        \begin{tabular}{ c c c }
            \faMobile\enspace +1 587-969-9556& \enspace\faEnvelope\enspace maridu.nageswararao@gmail.com& \enspace\faHome\enspace Calgary, Alberta, Canada\\
        \end{tabular}
    \end{center}
    \begin{center}
        \begin{tabular}{ c c c }
            \faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/nrmaridu/}{in/nrmaridu} &
            \enspace \faGithub\enspace \color{blue} \href{https://github.com/nrmaridu}{github.com/nrmaridu} &
            \enspace \faLanguage\enspace \color{blue} \href{https://www.loc.gov/standards/iso639-2/php/langcodes_name.php?iso_639_1=en}{en},
            \href{https://www.loc.gov/standards/iso639-2/php/langcodes_name.php?iso_639_1=te}{te}
        \end{tabular}
    \end{center}
    \section{Profile}
    {Results-oriented and innovative Senior Software Engineer with nearly \textbf{10} years of
    expertise, specializing in building large scale cloud native SaaS solutions with \textbf{microservices} architecture.
    Responsible and articulate individual with strengths in System Design, Solution Optimization, Cloud, Microservices architecture and Domain Driven Design.}
    \vspace{0.5em}

    {Seeking a challenging senior/lead role in distributed system projects where I can utilize my
    experience to drive innovation and contribute to the success of projects.}

    \section{Areas of Expertise}
    {Software Development - Distributed Systems - Microservices - Cloud Computing - Object Oriented Design - Concurrent Programming - REST - Event Driven Architecture - IAM - DDD - TDD}


    \section{Work Experience}

    \customcventry{Jan 2022 ‐ Present}{{\color{blue}\href{https://www.synopsys.com/}{Synopsys Canada}}}{Staff Software Engineer}{Calgary, AB, Canada}{}{}

    \customcventry{Dec 2016 ‐ Jan 2022}{{\color{blue}\href{https://www.synopsys.com/}{Synopsys India Pvt Ltd}}}{Senior Software Engineer}{Bangalore, KA, India}{}{}

    \customcventry{June 2016 ‐ Nov 2016}{{\color{blue}\href{https://www.synopsys.com/}{Cigital Asia Pvt Ltd (now Synopsys)}}}{Associate Software Engineer}{Bangalore, KA, India}{}{}

    \customcventry{Oct 2014 ‐ May 2016}{{\color{blue}\href{https://atos.net/en/}{Syntel Pvt Ltd  (now Atos)}}}{Application Programmer}{Chennai,TN, India}{}{}


    \section{Projects}

    \project{Project Title}{2020-2022}
    {This is a brief description of the project. It explains the main objectives and outcomes of the project.}
    {Java, Spring Boot, MySQL, Docker}
    {
        \item Developed RESTful APIs using Spring Boot.
        \item Designed and implemented database schema in MySQL.
        \item Containerized the application using Docker.
        \item Collaborated with the frontend team to integrate APIs.
    }

    \project{Another Project}{2018-2020}
    {This is another project description. It highlights the key features and achievements of the project.}
    {Python, Django, PostgreSQL, Kubernetes}
    {
        \item Built web applications using Django framework.
        \item Managed PostgreSQL databases and optimized queries.
        \item Deployed applications on Kubernetes clusters.
        \item Automated CI/CD pipelines using Jenkins.
    }

    % Polaris NG Project
    \customcventry{01/2022 ‐ present}{{\color{blue}{(Synopsys Canada)}}}{Polaris Nextgen}{}{}{
            {\projectdesc{Polaris is an integrated, cloud-based SaaS application security testing solution designed specifically for DevSecOps and development teams.
        I'm the lead developer responsible for design and development of SCM integration, Audit, Notification and IAM microservices for the platform.\newline{}}}
            {\textbf{Stack: Java, Golang, Spring Boot, Postgres, jOOQ, Rabbit MQ, Redis, Kubernetes, Datadog, RHSSO, Auth0 }
        }
            {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
                 \item hello.
                 \item Developed and implemented digital marketing strategies that generated over \$850,000 in revenue in 2023
                 \item Oversee the execution of SEO, SEM, email, social media, and display advertising campaigns, achieving a 12\% decrease in cost per acquisition
        \end{itemize}}}

    \vspace{1em}
    \customcventry{01/2017 ‐ 01/2022}{{\color{blue}{(Synopsys India)}}}{Reporting Platform}{}{}{
            {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
                 \item Implemented promotional activities such as re-targeting campaigns for e-commerce businesses.
                 \item Monitored the performance of PPC campaigns through Google Adwords.
                 \item Managed and optimized PPC campaigns, resulting in a 5\% increase in click-through rates.
        \end{itemize}}}

    \vspace{1em}

    \customcventry{June 2016 ‐ Feb 2018}{{\color{blue}{(Cigital, Synopsys)}}}{Software Security Applications}{}{}
    {
        \vspace{0.5em}
        {As a Full Stack Developer at Cigital, I contributed to the development of several software security applications, including:}
        {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
             \item \textbf{mySSI :} Platform for managing Secure Software Development Lifecycle(SSDLC) activities of software projects.
             \item \textbf{CEDAR :} A web application for scheduling penetration tests and managing test reports.
             \item \textbf{Secure Assist :} An on-premise static code analysis platform for softwares.
        \end{itemize}}
        {\textbf{Stack: Java, Spring Boot, JSP, MySQL, REST API, JavaScript, Bootstrap, Angular 2+ }}
        \\
        {\hspace{1em}\textbf{Key Responsibilities:}}
        {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
             \item Designed and developed multiple full-stack applications using a range of technologies..
             \item Led the transformation of a JavaScript based frontend application to Angular 2+ for a project, while assisting fellow developers in writing efficient and maintainable code.
             \item Made a significant impact by quickly acquiring expertise in Angular 2+, leveraging it's features and best practices to drive project success.
             \item Demonstrated expertise in migrating existing authorization model from RBAC to the new PBAC model using spring security framework.
        \end{itemize}}
    }

    \vspace{1em}
    \customcventry{Oct 2014 ‐ May 2016}{{\color{blue}{(Syntel Pvt)}}}{Plan Sponsor Application Suite}{}{}{
            {In my early years as a software professional, I worked as an outsourced Applications Programmer for Manulife, a Canadian multinational insurance company in modernizing their retirement plan service applications.}
            {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
                 \item Enhanced multiple backend applications to improve performance and efficiency..
                 \item Migrated the legacy HTML/CSS based front-end to a modern Bootstrap 5 based frontend, ensuring a seamless user experience across multiple browsers.
                 \item Designed multi-browser compatible UI components using JavaScript and jQuery, streamlining the development process.
                 \item Developed shell scripts and Ant scripts to automate local development processes, significantly increasing developer productivity.
        \end{itemize}}
            {This project showcases my early beginnings in the software industry, highlighting my ability to work on diverse tasks, from backend
        enhancements to frontend migrations, while also demonstrating my passion for process improvement and automation.}
    }


    \section{Education}
    \customcventry{2008-2014}{\color{blue}\href{https://www.google.com/}{Rajiv Gandhi University of Knowledge Technologies}}{Integrated Dual Degree}{Nuzvid, India}{}{CGPA : 8.15/10}{Bachelor of Technology in Computer Science \& Engineering | Minor in Management Studies.}

    \section{Skills}
    {\begin{itemize}[label=\textbullet]
         \itemsep0em
         \item {\textbf{Java}(primary), \textbf{Golang}, Python, JavaScript}
         \item {\textbf{PostgreSQL}, MySQL}
         \item {\textbf{RabbitMQ, Redis, Kubernetes(GCP), Docker, Datadog(Log Monitoring)}}
         \item {\textbf{REST}, gRPC API development}
         \item {Event Driven \textbf{Microservices} Development }
         \item {\textbf{Domain Driven Design}}
    \end{itemize}}


    \section{Achievements}
    \customcventry{Oct 2023}{{\color{blue}\href{https://www.synopsys.com/}{(Synopsys Inc)}}}{Ace Award}{Calgary, AB, Canada}{}{
            {Awarded the Ace Award for Outstanding Performance, recognizing my exceptional contributions to the team. Notable achievements include:}
            {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
                 \item Rapidly gaining expertise in Audit and Notifications domains, consistently delivering crucial features.
                 \item Successfully addressing complex consumer issues that significantly contributed to closing major deals.
                 \item Improving system design to accommodate innovative solutions, ensuring smooth progression of essential functionalities.
        \end{itemize}}
        \text{This achievement showcases my ability to adapt quickly, think critically, and drive results.}
    }

    \vspace{1em}

    \customcventry{Aug 2019}
    {{\color{blue}\href{https://www.synopsys.com/}{(Synopsys Inc)}}}{Star Award}{Bangalore, KA, India}{}{
            {Recipient of the Star Award in individual category, recognizing my extraordinary performance in designing and developing the Reporting Platform for Software Security Vulnerabilities. Notable achievements include:}
            {\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
                 \item Played a crucial role in designing and implementing the reporting platform, extracting data from multiple sources using batch pattern within a short span.
                 \item Demonstrated exceptional expertise and problem-solving skills in integrating diverse data streams to provide actionable insights.
        \end{itemize}}
            {This achievement highlights my ability to drive complex projects forward, think creatively, and deliver high-quality results
        under tight deadlines.}
    }

\end{document}

